Looking for a Signal in the Noise: Revisiting Obesity and the Microbiome

### 2016-07-19 submission/Sze_Obesity_mBio_2016.tex
Re-run make write.paper

\documentclass[12pt,]{article}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
  \newcommand{\euro}{€}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\usepackage[margin=1.0in]{geometry}
\usepackage{hyperref}
\PassOptionsToPackage{usenames,dvipsnames}{color} % color is loaded by hyperref
\hypersetup{unicode=true,
            pdfborder={0 0 0},
            breaklinks=true}
\urlstyle{same}  % don't use monospace font for urls
\usepackage{graphicx,grffile}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{0}

@@

\begin{document}

@@

\subsection*{References}\label{references}
\addcontentsline{toc}{subsection}{References}

\hypertarget{refs}{}
\hypertarget{ref-ogdenux5fprevalenceux5f2014}{}
1. \textbf{Ogden CL}, \textbf{Carroll MD}, \textbf{Kit BK},
\textbf{Flegal KM}. 2014. Prevalence of childhood and adult obesity in
the United States, 2011-2012. JAMA \textbf{311}:806--814.
doi:\href{https://doi.org/10.1001/jama.2014.732}{10.1001/jama.2014.732}.

\hypertarget{ref-lichtashux5fbodyux5f2013}{}
2. \textbf{Lichtash CT}, \textbf{Cui J}, \textbf{Guo X}, \textbf{Chen
Y-DI}, \textbf{Hsueh WA}, \textbf{Rotter JI}, \textbf{Goodarzi MO}.
2013. Body adiposity index versus body mass index and other
anthropometric traits as correlates of cardiometabolic risk factors.
PloS One \textbf{8}:e65954.
doi:\href{https://doi.org/10.1371/journal.pone.0065954}{10.1371/journal.pone.0065954}.

\hypertarget{ref-braheux5fcanux5f2016}{}
3. \textbf{Brahe LK}, \textbf{Astrup A}, \textbf{Larsen LH}. 2016. Can
We Prevent Obesity-Related Metabolic Diseases by Dietary Modulation of
the Gut Microbiota? Advances in Nutrition (Bethesda, Md)
\textbf{7}:90--101.
doi:\href{https://doi.org/10.3945/an.115.010587}{10.3945/an.115.010587}.

\hypertarget{ref-drorux5fmicrobiotaux5f2016}{}
4. \textbf{Dror T}, \textbf{Dickstein Y}, \textbf{Dubourg G},
\textbf{Paul M}. 2016. Microbiota manipulation for weight change.
Microbial Pathogenesis.
doi:\href{https://doi.org/10.1016/j.micpath.2016.01.002}{10.1016/j.micpath.2016.01.002}.

\hypertarget{ref-leyux5fobesityux5f2005}{}
5. \textbf{Ley RE}, \textbf{Bäckhed F}, \textbf{Turnbaugh P},
\textbf{Lozupone CA}, \textbf{Knight RD}, \textbf{Gordon JI}. 2005.
Obesity alters gut microbial ecology. Proceedings of the National
Academy of Sciences of the United States of America
\textbf{102}:11070--11075.
doi:\href{https://doi.org/10.1073/pnas.0504978102}{10.1073/pnas.0504978102}.

\hypertarget{ref-turnbaughux5fcoreux5f2009}{}
6. \textbf{Turnbaugh PJ}, \textbf{Hamady M}, \textbf{Yatsunenko T},
\textbf{Cantarel BL}, \textbf{Duncan A}, \textbf{Ley RE}, \textbf{Sogin
ML}, \textbf{Jones WJ}, \textbf{Roe BA}, \textbf{Affourtit JP},
\textbf{Egholm M}, \textbf{Henrissat B}, \textbf{Heath AC},
\textbf{Knight R}, \textbf{Gordon JI}. 2009. A core gut microbiome in
obese and lean twins. Nature \textbf{457}:480--484.
doi:\href{https://doi.org/10.1038/nature07540}{10.1038/nature07540}.

\hypertarget{ref-leyux5fmicrobialux5f2006}{}
7. \textbf{Ley RE}, \textbf{Turnbaugh PJ}, \textbf{Klein S},
\textbf{Gordon JI}. 2006. Microbial ecology: Human gut microbes
associated with obesity. Nature \textbf{444}:1022--1023.
doi:\href{https://doi.org/10.1038/4441022a}{10.1038/4441022a}.

\hypertarget{ref-waltersux5fmeta-analysesux5f2014}{}
8. \textbf{Walters WA}, \textbf{Xu Z}, \textbf{Knight R}. 2014.
Meta-analyses of human gut microbes associated with obesity and IBD.
FEBS letters \textbf{588}:4223--4233.
doi:\href{https://doi.org/10.1016/j.febslet.2014.09.039}{10.1016/j.febslet.2014.09.039}.

\hypertarget{ref-finucaneux5ftaxonomicux5f2014}{}
9. \textbf{Finucane MM}, \textbf{Sharpton TJ}, \textbf{Laurent TJ},
\textbf{Pollard KS}. 2014. A taxonomic signature of obesity in the
microbiome? Getting to the guts of the matter. PloS One
\textbf{9}:e84689.
doi:\href{https://doi.org/10.1371/journal.pone.0084689}{10.1371/journal.pone.0084689}.

\hypertarget{ref-turnbaughux5fobesity-associatedux5f2006}{}
10. \textbf{Turnbaugh PJ}, \textbf{Ley RE}, \textbf{Mahowald MA},
\textbf{Magrini V}, \textbf{Mardis ER}, \textbf{Gordon JI}. 2006. An
obesity-associated gut microbiome with increased capacity for energy
harvest. Nature \textbf{444}:1027--31.
doi:\href{https://doi.org/10.1038/nature05414}{10.1038/nature05414}.

\hypertarget{ref-Koren2012}{}
11. \textbf{Koren O}, \textbf{Goodrich JK}, \textbf{Cullender TC},
\textbf{Spor A}, \textbf{Laitinen K}, \textbf{Bäckhed HK},
\textbf{Gonzalez A}, \textbf{Werner JJ}, \textbf{Angenent LT},
\textbf{Knight R}, \textbf{Bäckhed F}, \textbf{Isolauri E},
\textbf{Salminen S}, \textbf{Ley RE}. 2012. Host remodeling of the gut
microbiome and metabolic changes during pregnancy. Cell
\textbf{150}:470--480.
doi:\href{https://doi.org/10.1016/j.cell.2012.07.008}{10.1016/j.cell.2012.07.008}.

\hypertarget{ref-Cox2014}{}
12. \textbf{Cox LM}, \textbf{Yamanishi S}, \textbf{Sohn J},
\textbf{Alekseyenko AV}, \textbf{Leung JM}, \textbf{Cho I}, \textbf{Kim
SG}, \textbf{Li H}, \textbf{Gao Z}, \textbf{Mahana D}, \textbf{Rodriguez
JGZ}, \textbf{Rogers AB}, \textbf{Robine N}, \textbf{Loke P},
\textbf{Blaser MJ}. 2014. Altering the intestinal microbiota during a
critical developmental window has lasting metabolic consequences. Cell
\textbf{158}:705--721.
doi:\href{https://doi.org/10.1016/j.cell.2014.05.052}{10.1016/j.cell.2014.05.052}.

\hypertarget{ref-Mahana2016}{}
13. \textbf{Mahana D}, \textbf{Trent CM}, \textbf{Kurtz ZD},
\textbf{Bokulich NA}, \textbf{Battaglia T}, \textbf{Chung J},
\textbf{Müller CL}, \textbf{Li H}, \textbf{Bonneau RA}, \textbf{Blaser
MJ}. 2016. Antibiotic perturbation of the murine gut microbiome enhances
the adiposity, insulin resistance, and liver disease associated with
high-fat diet. Genome Medicine \textbf{8}.
doi:\href{https://doi.org/10.1186/s13073-016-0297-9}{10.1186/s13073-016-0297-9}.

\hypertarget{ref-moherux5fpreferredux5f2010}{}
14. \textbf{Moher D}, \textbf{Liberati A}, \textbf{Tetzlaff J},
\textbf{Altman DG}, \textbf{PRISMA Group}. 2010. Preferred reporting
items for systematic reviews and meta-analyses: The PRISMA statement.
International Journal of Surgery (London, England) \textbf{8}:336--341.
doi:\href{https://doi.org/10.1016/j.ijsu.2010.02.007}{10.1016/j.ijsu.2010.02.007}.

\hypertarget{ref-zupancicux5fanalysisux5f2012}{}
15. \textbf{Zupancic ML}, \textbf{Cantarel BL}, \textbf{Liu Z},
\textbf{Drabek EF}, \textbf{Ryan KA}, \textbf{Cirimotich S},
\textbf{Jones C}, \textbf{Knight R}, \textbf{Walters WA},
\textbf{Knights D}, \textbf{Mongodin EF}, \textbf{Horenstein RB},
\textbf{Mitchell BD}, \textbf{Steinle N}, \textbf{Snitker S},
\textbf{Shuldiner AR}, \textbf{Fraser CM}. 2012. Analysis of the gut
microbiota in the old order Amish and its relation to the metabolic
syndrome. PloS One \textbf{7}:e43052.
doi:\href{https://doi.org/10.1371/journal.pone.0043052}{10.1371/journal.pone.0043052}.

\hypertarget{ref-escobarux5fgutux5f2014}{}
16. \textbf{Escobar JS}, \textbf{Klotz B}, \textbf{Valdes BE},
\textbf{Agudelo GM}. 2014. The gut microbiota of Colombians differs from
that of Americans, Europeans and Asians. BMC microbiology
\textbf{14}:311.
doi:\href{https://doi.org/10.1186/s12866-014-0311-6}{10.1186/s12866-014-0311-6}.

\hypertarget{ref-zeeviux5fpersonalizedux5f2015}{}
17. \textbf{Zeevi D}, \textbf{Korem T}, \textbf{Zmora N},
\textbf{Israeli D}, \textbf{Rothschild D}, \textbf{Weinberger A},
\textbf{Ben-Yacov O}, \textbf{Lador D}, \textbf{Avnit-Sagi T},
\textbf{Lotan-Pompan M}, \textbf{Suez J}, \textbf{Mahdi JA},
\textbf{Matot E}, \textbf{Malka G}, \textbf{Kosower N}, \textbf{Rein M},
\textbf{Zilberman-Schapira G}, \textbf{Dohnalová L},
\textbf{Pevsner-Fischer M}, \textbf{Bikovsky R}, \textbf{Halpern Z},
\textbf{Elinav E}, \textbf{Segal E}. 2015. Personalized Nutrition by
Prediction of Glycemic Responses. Cell \textbf{163}:1079--1094.
doi:\href{https://doi.org/10.1016/j.cell.2015.11.001}{10.1016/j.cell.2015.11.001}.

\hypertarget{ref-rossux5f16sux5f2015}{}
18. \textbf{Ross MC}, \textbf{Muzny DM}, \textbf{McCormick JB},
\textbf{Gibbs RA}, \textbf{Fisher-Hoch SP}, \textbf{Petrosino JF}. 2015.
16S gut community of the Cameron County Hispanic Cohort. Microbiome
\textbf{3}:7.
doi:\href{https://doi.org/10.1186/s40168-015-0072-y}{10.1186/s40168-015-0072-y}.

\hypertarget{ref-goodrichux5fhumanux5f2014}{}
19. \textbf{Goodrich JK}, \textbf{Waters JL}, \textbf{Poole AC},
\textbf{Sutter JL}, \textbf{Koren O}, \textbf{Blekhman R},
\textbf{Beaumont M}, \textbf{Van Treuren W}, \textbf{Knight R},
\textbf{Bell JT}, \textbf{Spector TD}, \textbf{Clark AG}, \textbf{Ley
RE}. 2014. Human genetics shape the gut microbiome. Cell
\textbf{159}:789--799.
doi:\href{https://doi.org/10.1016/j.cell.2014.09.053}{10.1016/j.cell.2014.09.053}.

\hypertarget{ref-wuux5flinkingux5f2011}{}
20. \textbf{Wu GD}, \textbf{Chen J}, \textbf{Hoffmann C},
\textbf{Bittinger K}, \textbf{Chen Y-Y}, \textbf{Keilbaugh SA},
\textbf{Bewtra M}, \textbf{Knights D}, \textbf{Walters WA},
\textbf{Knight R}, \textbf{Sinha R}, \textbf{Gilroy E}, \textbf{Gupta
K}, \textbf{Baldassano R}, \textbf{Nessel L}, \textbf{Li H},
\textbf{Bushman FD}, \textbf{Lewis JD}. 2011. Linking long-term dietary
patterns with gut microbial enterotypes. Science (New York, NY)
\textbf{334}:105--108.
doi:\href{https://doi.org/10.1126/science.1208344}{10.1126/science.1208344}.

\hypertarget{ref-humanux5fmicrobiomeux5fprojectux5fconsortiumux5fstructureux5f2012}{}
21. \textbf{Human Microbiome Project Consortium}. 2012. Structure,
function and diversity of the healthy human microbiome. Nature
\textbf{486}:207--214.
doi:\href{https://doi.org/10.1038/nature11234}{10.1038/nature11234}.

\hypertarget{ref-schubertux5fmicrobiomeux5f2014}{}
22. \textbf{Schubert AM}, \textbf{Rogers MAM}, \textbf{Ring C},
\textbf{Mogle J}, \textbf{Petrosino JP}, \textbf{Young VB},
\textbf{Aronoff DM}, \textbf{Schloss PD}. 2014. Microbiome data
distinguish patients with Clostridium difficile infection and non-C.
difficile-associated diarrhea from healthy controls. mBio
\textbf{5}:e01021--01014.
doi:\href{https://doi.org/10.1128/mBio.01021-14}{10.1128/mBio.01021-14}.

\hypertarget{ref-baxterux5fmicrobiota-basedux5f2016}{}
23. \textbf{Baxter NT}, \textbf{Ruffin MT}, \textbf{Rogers MAM},
\textbf{Schloss PD}. 2016. Microbiota-based model improves the
sensitivity of fecal immunochemical test for detecting colonic lesions.
Genome Medicine \textbf{8}:37.
doi:\href{https://doi.org/10.1186/s13073-016-0290-3}{10.1186/s13073-016-0290-3}.

\hypertarget{ref-Kozichux5f2013}{}
24. \textbf{Kozich JJ}, \textbf{Westcott SL}, \textbf{Baxter NT},
\textbf{Highlander SK}, \textbf{Schloss PD}. 2013. Development of a
dual-index sequencing strategy and curation pipeline for analyzing
amplicon sequence data on the MiSeq Illumina sequencing platform.
Applied and environmental microbiology \textbf{79}:5112--5120.

\hypertarget{ref-Schloss2011}{}
25. \textbf{Schloss PD}, \textbf{Gevers D}, \textbf{Westcott SL}. 2011.
Reducing the effects of PCR amplification and sequencing artifacts on
16S rRNA-based studies. PLoS ONE \textbf{6}:e27310.
doi:\href{https://doi.org/10.1371/journal.pone.0027310}{10.1371/journal.pone.0027310}.

\hypertarget{ref-Westcott2015}{}
26. \textbf{Westcott SL}, \textbf{Schloss PD}. 2015. De novo clustering
methods outperform reference-based methods for assigning 16S rRNA gene
sequences to operational taxonomic units. PeerJ \textbf{3}:e1487.
doi:\href{https://doi.org/10.7717/peerj.1487}{10.7717/peerj.1487}.

\hypertarget{ref-Wang2007}{}
27. \textbf{Wang Q}, \textbf{Garrity GM}, \textbf{Tiedje JM},
\textbf{Cole JR}. 2007. Naive bayesian classifier for rapid assignment
of rRNA sequences into the new bacterial taxonomy. Applied and
Environmental Microbiology \textbf{73}:5261--5267.
doi:\href{https://doi.org/10.1128/aem.00062-07}{10.1128/aem.00062-07}.

>>>>

\documentclass[12pt,]{article}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
    \usepackage{xltxtra,xunicode}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Mapping=tex-text,Scale=MatchLowercase}
  \newcommand{\euro}{€}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\usepackage[margin=1.0in]{geometry}
\ifxetex
  \usepackage[setpagesize=false, % page size defined by xetex
              unicode=false, % unicode breaks when used with xetex
              xetex]{hyperref}
\else
  \usepackage[unicode=true]{hyperref}
\fi
\hypersetup{breaklinks=true,
            bookmarks=true,
            pdfauthor={},
            pdftitle={},
            colorlinks=true,
            citecolor=blue,
            urlcolor=blue,
            linkcolor=magenta,
            pdfborder={0 0 0}}
\urlstyle{same}  % don't use monospace font for urls
\usepackage{graphicx,grffile}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{0}

@@

\begin{document}
\maketitle

@@

\hyperdef{}{references}{\label{references}}
\subsection*{References}\label{references}
\addcontentsline{toc}{subsection}{References}

\hyperdef{}{ref-ogdenux5fprevalenceux5f2014}{\label{ref-ogdenux5fprevalenceux5f2014}}
1. \textbf{Ogden CL}, \textbf{Carroll MD}, \textbf{Kit BK},
\textbf{Flegal KM}. 2014. Prevalence of childhood and adult obesity in
the United States, 2011-2012. JAMA \textbf{311}:806--814.
doi:\url{http://doi.org/10.1001/jama.2014.732}.

\hyperdef{}{ref-lichtashux5fbodyux5f2013}{\label{ref-lichtashux5fbodyux5f2013}}
2. \textbf{Lichtash CT}, \textbf{Cui J}, \textbf{Guo X}, \textbf{Chen
Y-DI}, \textbf{Hsueh WA}, \textbf{Rotter JI}, \textbf{Goodarzi MO}.
2013. Body adiposity index versus body mass index and other
anthropometric traits as correlates of cardiometabolic risk factors.
PloS One \textbf{8}:e65954.
doi:\url{http://doi.org/10.1371/journal.pone.0065954}.

\hyperdef{}{ref-braheux5fcanux5f2016}{\label{ref-braheux5fcanux5f2016}}
3. \textbf{Brahe LK}, \textbf{Astrup A}, \textbf{Larsen LH}. 2016. Can
We Prevent Obesity-Related Metabolic Diseases by Dietary Modulation of
the Gut Microbiota? Advances in Nutrition (Bethesda, Md)
\textbf{7}:90--101. doi:\url{http://doi.org/10.3945/an.115.010587}.

\hyperdef{}{ref-drorux5fmicrobiotaux5f2016}{\label{ref-drorux5fmicrobiotaux5f2016}}
4. \textbf{Dror T}, \textbf{Dickstein Y}, \textbf{Dubourg G},
\textbf{Paul M}. 2016. Microbiota manipulation for weight change.
Microbial Pathogenesis.
doi:\url{http://doi.org/10.1016/j.micpath.2016.01.002}.

\hyperdef{}{ref-leyux5fobesityux5f2005}{\label{ref-leyux5fobesityux5f2005}}
5. \textbf{Ley RE}, \textbf{Bäckhed F}, \textbf{Turnbaugh P},
\textbf{Lozupone CA}, \textbf{Knight RD}, \textbf{Gordon JI}. 2005.
Obesity alters gut microbial ecology. Proceedings of the National
Academy of Sciences of the United States of America
\textbf{102}:11070--11075.
doi:\url{http://doi.org/10.1073/pnas.0504978102}.

\hyperdef{}{ref-turnbaughux5fcoreux5f2009}{\label{ref-turnbaughux5fcoreux5f2009}}
6. \textbf{Turnbaugh PJ}, \textbf{Hamady M}, \textbf{Yatsunenko T},
\textbf{Cantarel BL}, \textbf{Duncan A}, \textbf{Ley RE}, \textbf{Sogin
ML}, \textbf{Jones WJ}, \textbf{Roe BA}, \textbf{Affourtit JP},
\textbf{Egholm M}, \textbf{Henrissat B}, \textbf{Heath AC},
\textbf{Knight R}, \textbf{Gordon JI}. 2009. A core gut microbiome in
obese and lean twins. Nature \textbf{457}:480--484.
doi:\url{http://doi.org/10.1038/nature07540}.

\hyperdef{}{ref-leyux5fmicrobialux5f2006}{\label{ref-leyux5fmicrobialux5f2006}}
7. \textbf{Ley RE}, \textbf{Turnbaugh PJ}, \textbf{Klein S},
\textbf{Gordon JI}. 2006. Microbial ecology: Human gut microbes
associated with obesity. Nature \textbf{444}:1022--1023.
doi:\url{http://doi.org/10.1038/4441022a}.

\hyperdef{}{ref-waltersux5fmeta-analysesux5f2014}{\label{ref-waltersux5fmeta-analysesux5f2014}}
8. \textbf{Walters WA}, \textbf{Xu Z}, \textbf{Knight R}. 2014.
Meta-analyses of human gut microbes associated with obesity and IBD.
FEBS letters \textbf{588}:4223--4233.
doi:\url{http://doi.org/10.1016/j.febslet.2014.09.039}.

\hyperdef{}{ref-finucaneux5ftaxonomicux5f2014}{\label{ref-finucaneux5ftaxonomicux5f2014}}
9. \textbf{Finucane MM}, \textbf{Sharpton TJ}, \textbf{Laurent TJ},
\textbf{Pollard KS}. 2014. A taxonomic signature of obesity in the
microbiome? Getting to the guts of the matter. PloS One
\textbf{9}:e84689.
doi:\url{http://doi.org/10.1371/journal.pone.0084689}.

\hyperdef{}{ref-turnbaughux5fobesity-associatedux5f2006}{\label{ref-turnbaughux5fobesity-associatedux5f2006}}
10. \textbf{Turnbaugh PJ}, \textbf{Ley RE}, \textbf{Mahowald MA},
\textbf{Magrini V}, \textbf{Mardis ER}, \textbf{Gordon JI}. 2006. An
obesity-associated gut microbiome with increased capacity for energy
harvest. Nature \textbf{444}:1027--31.
doi:\url{http://doi.org/10.1038/nature05414}.

\hyperdef{}{ref-Koren2012}{\label{ref-Koren2012}}
11. \textbf{Koren O}, \textbf{Goodrich JK}, \textbf{Cullender TC},
\textbf{Spor A}, \textbf{Laitinen K}, \textbf{Bäckhed HK},
\textbf{Gonzalez A}, \textbf{Werner JJ}, \textbf{Angenent LT},
\textbf{Knight R}, \textbf{Bäckhed F}, \textbf{Isolauri E},
\textbf{Salminen S}, \textbf{Ley RE}. 2012. Host remodeling of the gut
microbiome and metabolic changes during pregnancy. Cell
\textbf{150}:470--480.
doi:\url{http://doi.org/10.1016/j.cell.2012.07.008}.

\hyperdef{}{ref-Cox2014}{\label{ref-Cox2014}}
12. \textbf{Cox LM}, \textbf{Yamanishi S}, \textbf{Sohn J},
\textbf{Alekseyenko AV}, \textbf{Leung JM}, \textbf{Cho I}, \textbf{Kim
SG}, \textbf{Li H}, \textbf{Gao Z}, \textbf{Mahana D}, \textbf{Rodriguez
JGZ}, \textbf{Rogers AB}, \textbf{Robine N}, \textbf{Loke P},
\textbf{Blaser MJ}. 2014. Altering the intestinal microbiota during a
critical developmental window has lasting metabolic consequences. Cell
\textbf{158}:705--721.
doi:\url{http://doi.org/10.1016/j.cell.2014.05.052}.

\hyperdef{}{ref-Mahana2016}{\label{ref-Mahana2016}}
13. \textbf{Mahana D}, \textbf{Trent CM}, \textbf{Kurtz ZD},
\textbf{Bokulich NA}, \textbf{Battaglia T}, \textbf{Chung J},
\textbf{Müller CL}, \textbf{Li H}, \textbf{Bonneau RA}, \textbf{Blaser
MJ}. 2016. Antibiotic perturbation of the murine gut microbiome enhances
the adiposity, insulin resistance, and liver disease associated with
high-fat diet. Genome Medicine \textbf{8}.
doi:\url{http://doi.org/10.1186/s13073-016-0297-9}.

\hyperdef{}{ref-moherux5fpreferredux5f2010}{\label{ref-moherux5fpreferredux5f2010}}
14. \textbf{Moher D}, \textbf{Liberati A}, \textbf{Tetzlaff J},
\textbf{Altman DG}, \textbf{PRISMA Group}. 2010. Preferred reporting
items for systematic reviews and meta-analyses: The PRISMA statement.
International Journal of Surgery (London, England) \textbf{8}:336--341.
doi:\url{http://doi.org/10.1016/j.ijsu.2010.02.007}.

\hyperdef{}{ref-zupancicux5fanalysisux5f2012}{\label{ref-zupancicux5fanalysisux5f2012}}
15. \textbf{Zupancic ML}, \textbf{Cantarel BL}, \textbf{Liu Z},
\textbf{Drabek EF}, \textbf{Ryan KA}, \textbf{Cirimotich S},
\textbf{Jones C}, \textbf{Knight R}, \textbf{Walters WA},
\textbf{Knights D}, \textbf{Mongodin EF}, \textbf{Horenstein RB},
\textbf{Mitchell BD}, \textbf{Steinle N}, \textbf{Snitker S},
\textbf{Shuldiner AR}, \textbf{Fraser CM}. 2012. Analysis of the gut
microbiota in the old order Amish and its relation to the metabolic
syndrome. PloS One \textbf{7}:e43052.
doi:\url{http://doi.org/10.1371/journal.pone.0043052}.

\hyperdef{}{ref-escobarux5fgutux5f2014}{\label{ref-escobarux5fgutux5f2014}}
16. \textbf{Escobar JS}, \textbf{Klotz B}, \textbf{Valdes BE},
\textbf{Agudelo GM}. 2014. The gut microbiota of Colombians differs from
that of Americans, Europeans and Asians. BMC microbiology
\textbf{14}:311. doi:\url{http://doi.org/10.1186/s12866-014-0311-6}.

\hyperdef{}{ref-zeeviux5fpersonalizedux5f2015}{\label{ref-zeeviux5fpersonalizedux5f2015}}
17. \textbf{Zeevi D}, \textbf{Korem T}, \textbf{Zmora N},
\textbf{Israeli D}, \textbf{Rothschild D}, \textbf{Weinberger A},
\textbf{Ben-Yacov O}, \textbf{Lador D}, \textbf{Avnit-Sagi T},
\textbf{Lotan-Pompan M}, \textbf{Suez J}, \textbf{Mahdi JA},
\textbf{Matot E}, \textbf{Malka G}, \textbf{Kosower N}, \textbf{Rein M},
\textbf{Zilberman-Schapira G}, \textbf{Dohnalová L},
\textbf{Pevsner-Fischer M}, \textbf{Bikovsky R}, \textbf{Halpern Z},
\textbf{Elinav E}, \textbf{Segal E}. 2015. Personalized Nutrition by
Prediction of Glycemic Responses. Cell \textbf{163}:1079--1094.
doi:\url{http://doi.org/10.1016/j.cell.2015.11.001}.

\hyperdef{}{ref-rossux5f16sux5f2015}{\label{ref-rossux5f16sux5f2015}}
18. \textbf{Ross MC}, \textbf{Muzny DM}, \textbf{McCormick JB},
\textbf{Gibbs RA}, \textbf{Fisher-Hoch SP}, \textbf{Petrosino JF}. 2015.
16S gut community of the Cameron County Hispanic Cohort. Microbiome
\textbf{3}:7. doi:\url{http://doi.org/10.1186/s40168-015-0072-y}.

\hyperdef{}{ref-goodrichux5fhumanux5f2014}{\label{ref-goodrichux5fhumanux5f2014}}
19. \textbf{Goodrich JK}, \textbf{Waters JL}, \textbf{Poole AC},
\textbf{Sutter JL}, \textbf{Koren O}, \textbf{Blekhman R},
\textbf{Beaumont M}, \textbf{Van Treuren W}, \textbf{Knight R},
\textbf{Bell JT}, \textbf{Spector TD}, \textbf{Clark AG}, \textbf{Ley
RE}. 2014. Human genetics shape the gut microbiome. Cell
\textbf{159}:789--799.
doi:\url{http://doi.org/10.1016/j.cell.2014.09.053}.

\hyperdef{}{ref-wuux5flinkingux5f2011}{\label{ref-wuux5flinkingux5f2011}}
20. \textbf{Wu GD}, \textbf{Chen J}, \textbf{Hoffmann C},
\textbf{Bittinger K}, \textbf{Chen Y-Y}, \textbf{Keilbaugh SA},
\textbf{Bewtra M}, \textbf{Knights D}, \textbf{Walters WA},
\textbf{Knight R}, \textbf{Sinha R}, \textbf{Gilroy E}, \textbf{Gupta
K}, \textbf{Baldassano R}, \textbf{Nessel L}, \textbf{Li H},
\textbf{Bushman FD}, \textbf{Lewis JD}. 2011. Linking long-term dietary
patterns with gut microbial enterotypes. Science (New York, NY)
\textbf{334}:105--108. doi:\url{http://doi.org/10.1126/science.1208344}.

\hyperdef{}{ref-humanux5fmicrobiomeux5fprojectux5fconsortiumux5fstructureux5f2012}{\label{ref-humanux5fmicrobiomeux5fprojectux5fconsortiumux5fstructureux5f2012}}
21. \textbf{Human Microbiome Project Consortium}. 2012. Structure,
function and diversity of the healthy human microbiome. Nature
\textbf{486}:207--214. doi:\url{http://doi.org/10.1038/nature11234}.

\hyperdef{}{ref-schubertux5fmicrobiomeux5f2014}{\label{ref-schubertux5fmicrobiomeux5f2014}}
22. \textbf{Schubert AM}, \textbf{Rogers MAM}, \textbf{Ring C},
\textbf{Mogle J}, \textbf{Petrosino JP}, \textbf{Young VB},
\textbf{Aronoff DM}, \textbf{Schloss PD}. 2014. Microbiome data
distinguish patients with Clostridium difficile infection and non-C.
difficile-associated diarrhea from healthy controls. mBio
\textbf{5}:e01021--01014.
doi:\url{http://doi.org/10.1128/mBio.01021-14}.

\hyperdef{}{ref-baxterux5fmicrobiota-basedux5f2016}{\label{ref-baxterux5fmicrobiota-basedux5f2016}}
23. \textbf{Baxter NT}, \textbf{Ruffin MT}, \textbf{Rogers MAM},
\textbf{Schloss PD}. 2016. Microbiota-based model improves the
sensitivity of fecal immunochemical test for detecting colonic lesions.
Genome Medicine \textbf{8}:37.
doi:\url{http://doi.org/10.1186/s13073-016-0290-3}.

\hyperdef{}{ref-Kozichux5f2013}{\label{ref-Kozichux5f2013}}
24. \textbf{Kozich JJ}, \textbf{Westcott SL}, \textbf{Baxter NT},
\textbf{Highlander SK}, \textbf{Schloss PD}. 2013. Development of a
dual-index sequencing strategy and curation pipeline for analyzing
amplicon sequence data on the MiSeq Illumina sequencing platform.
Applied and environmental microbiology \textbf{79}:5112--5120.

\hyperdef{}{ref-Schloss2011}{\label{ref-Schloss2011}}
25. \textbf{Schloss PD}, \textbf{Gevers D}, \textbf{Westcott SL}. 2011.
Reducing the effects of PCR amplification and sequencing artifacts on
16S rRNA-based studies. PLoS ONE \textbf{6}:e27310.
doi:\url{http://doi.org/10.1371/journal.pone.0027310}.

\hyperdef{}{ref-Westcott2015}{\label{ref-Westcott2015}}
26. \textbf{Westcott SL}, \textbf{Schloss PD}. 2015. De novo clustering
methods outperform reference-based methods for assigning 16S rRNA gene
sequences to operational taxonomic units. PeerJ \textbf{3}:e1487.
doi:\url{http://doi.org/10.7717/peerj.1487}.

\hyperdef{}{ref-Wang2007}{\label{ref-Wang2007}}
27. \textbf{Wang Q}, \textbf{Garrity GM}, \textbf{Tiedje JM},
\textbf{Cole JR}. 2007. Naive bayesian classifier for rapid assignment
of rRNA sequences into the new bacterial taxonomy. Applied and
Environmental Microbiology \textbf{73}:5261--5267.
doi:\url{http://doi.org/10.1128/aem.00062-07}.
